---
title: "Lab 01 - Hello R"
author: "Qilin Zhang"
date: "2023/1/2"
output: 
  html_document: 
    theme: journal
    fig_width: 9
    fig_height: 7
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

dim(datasaurus_dozen)
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)

datasaurus_dozen total: 1846x3
13 data sets and each has 142 data points

### Exercise 2

The answers for this exercise are given for you below.
But you should clean up some of the narrative so that it only includes what you want to turn in.

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


```{r plot-star}
plot_star <- datasaurus_dozen %>%
  filter(dataset=="star")

ggplot(data=plot_star, mapping=aes(x=x,y=y))+
  geom_point()

```

The correlation are very similar between star data and Dino data. They are both very close to none (r=-0.06)

```{r cor-star}
plot_star %>%
  summarize(r=cor(x,y))
```

### Exercise 4


```{r plot-circle}
plot_circle <- datasaurus_dozen %>%
  filter(dataset=="circle")

ggplot(data=plot_circle, mapping=aes(x=x , y=y))+
  geom_point()

```

The correlation are very similar between star data and Dino data. They are both very close to none (r=-0.06 to -0.07)

```{r cor-circle}
plot_circle %>%
  summarize(r=cor(x,y))
```

### Exercise 5

```{r everything all at once- plot, fig.height=7, fig.width=9}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point(size=1)+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r everything all at once - cor}
  datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```


## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
